Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-15 paper.tex
minor

%% Title information
\title[Garbage Collection Evaluation Infrastructure]{Garbage Collection Evaluation Infrastructure for the Cog VM}

@@

\paragraph{Stable heap.} The stable heap benchmarks perform random memory accesses in a heap which size remains approximately the same. We built one benchmark:

\begin{itemize}
	\item \emph{ExpandPropertiesWithCache}: computes all interesting properties of the model, common properties with low memory footprint are already cached and other properties are discarded once computed.
\end{itemize}

@@

It would be nice to evaluate both Sweeper and Planning on what we've just discussed.

>>>>

%% Title information
\title[Garbage Collection Evaluation Infrastructure]{Garbage Collection Evaluation Infrastructure\\ for the Cog VM}

@@

\paragraph{Stable heap.} The stable heap benchmarks perform random memory accesses in a heap which size remains approximately the same. We built one benchmark, \emph{ExpandPropertiesWithCache}, which computes all interesting properties of the model, common properties with low memory footprint are already cached and other properties are discarded once computed.

@@

\todo{Sophie}
It would be nice to evaluate both Sweeper and Planning on what we've just discussed.
